---
title: "The Analysis of Cycling Infrastructure in London, UK"
author: "Zeqiang Fang"
date: "2021/03/19"
output: html_document
---

Import the environment
```{r,message = FALSE,warning = FALSE,results='hide'}
library(tidyverse)
library(data.table)
library(sp)
library(sf)
library(table1)
library(tm)
library(spatstat)
library(here)
library(sp)
library(rgeos)
library(maptools)
library(tmap)
library(sf)
library(geojson)
library(geojsonio)
library(tmaptools)
library(RColorBrewer)
library(spdep) 
```

Import the London Boroughs
```{r}
# First, I get the London Boroughs' Boundaries
# Maybe it can be altered by Wards to do other fields of analysis
LondonBoroughs <- st_read(here::here("Dataset", "statistical-gis-boundaries-london", "ESRI", "London_Borough_Excluding_MHW.shp"))

library(stringr)
BoroughMap <- LondonBoroughs %>%
  dplyr::filter(str_detect(GSS_CODE, "^E09"))%>%
  st_transform(., 27700)

# Check if it can be run in the interactive map
tmap_mode("view")
qtm(BoroughMap)
```

## 1 Data Exploration

Utilise the CycleInfraLnd R package to access the dataset
```{r}
# CycleInfraLnd package is a very convenient package to get dataset from https://cycling.data.tfl.gov.uk/ Cycling infrastructure section

# The guidence to use CycleInfraLnd can be find in this link: https://github.com/PublicHealthDataGeek/CycleInfraLnd
library(CycleInfraLnd)
signal_point = get_cid_points(type = "signal") %>%
    st_transform(.,27700)
head(signal_point)
```
Cycling signal data is filtered by survey date (2017/2018)
SVDATE means the survey date for data record
```{r}
signal_point_17 = signal_point %>%
                filter(SVDATE < '2018-01-01')
signal_point_18 = signal_point %>%
                filter(SVDATE < "2019-01-01")
signal_point_18_plus = signal_point %>%
                filter(SVDATE > "2017-12-31")
summary(signal_point_17)
summary(signal_point_18)

# plot the data point for different recorded date
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(signal_point_17) +
  tm_dots(col = "blue") +
tm_shape(signal_point_18_plus) +
  tm_dots(col = "red")
```
We found the signal data for bikes is a small number for each borough. Cycling signals are frequently seen along the street in City of London, Westminster and 
Tower Hamlets where there are many tourist attractions.

Overview of Parking Point
```{r}
library(CycleInfraLnd)
parking_point = get_cid_points(type = "cycle_parking")%>%
    st_transform(.,27700)

# data inspects
parking_point %>% head()
nrow(parking_point)
ncol(parking_point)

# data slice by different survey date
parking_point_17 = parking_point %>%
                filter(SVDATE < '2018-01-01')
parking_point_18 = parking_point %>%
                filter(SVDATE < "2019-01-01")
parking_point_18_plus = parking_point %>%
                filter(SVDATE > "2017-12-31")
head(parking_point_17,5)
head(parking_point_18_plus,5)

# plot the map
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(parking_point_17) +
  tm_dots(col = "blue") +
tm_shape(parking_point_18_plus) +
  tm_dots(col = "red")
```


```{r}
# Data cleaning
library(tidyverse)
library(sf)
parking_point = distinct(parking_point)

#Adjust
parking_point_sub = parking_point[BoroughMap,]
#check to see that they've been removed
tmap_mode("view")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(parking_point_sub) +
  tm_dots(col = "blue")

```

# 2 The Density Analysis of Cycling Lane/Track

## 2.1 Line Data Exploration

```{r}
# The density of the number of cycling lanes
library(CycleInfraLnd)
cycle_lane = get_cid_lines("cycle_lane_track")
# make the lane dataset smaller
names(cycle_lane)
cycle_lane_slim = dplyr::select(cycle_lane,FEATURE_ID,BOROUGH,geometry)

# export the cycling lane map
tmap_mode("plot")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(cycle_lane_slim) +
  tm_lines(col = "blue")

```

## 2.2 Data preprocessing and merge
```{r}
# It is important to transform boroughs into GSS_Code to plot the map
# Firstly, we can inspect the boroughs value in nldf1 & MapBoroughs
# head(cycle_lane_slim$BOROUGH)
# head(BoroughMap$NAME)

# Also we need to transform "&" into "and" in nldf1 dataset
# BOROUGH == "Kensington & Chelsea"
# BOROUGH == "Barking & Dagenham"
# BOROUGH == "Hammersmith & Fulham"
# Utilise recode to apply find&replace operation

# "cldf" means "cycle line dataframe"
# utilise the recode methods
cldf = cycle_lane_slim %>% 
  mutate(BOROUGH = recode(BOROUGH, "Kensington & Chelsea"="Kensington and Chelsea")) %>%
  mutate(BOROUGH = recode(BOROUGH,"Barking & Dagenham"="Barking and Dagenham")) %>%
  mutate(BOROUGH = recode(BOROUGH,"Hammersmith & Fulha"="Hammersmith and Fulha"))

# cldf1  = cldf %>% select(., FEATURE_ID,SVDATE,CLT_COLOUR,BOROUGH)
# we need to drop the geometry attribute in the beginning
# replace the column name "BOROUGH" into "NAME"
cldf1 = cycle_lane_slim %>% st_drop_geometry()
cldf1 = rename(cldf1, NAME = BOROUGH)

# Merge the dataframe
cldf_merged = merge(LondonBoroughs, cldf1 ,by="NAME",all = TRUE)
```

## 2.3 The statistics analysis of the cycling lane for boroughs
```{r}
# inspect the names of cycle_lane
names(cldf_merged)

# the number of lane dataframe
nldf = cldf_merged %>%
  add_count(GSS_CODE) %>%
  mutate(area = st_area(.)) %>%
  mutate(density = n*1000*1000 / area)


nldf1 = dplyr::select(nldf,density,NAME,GSS_CODE, n)

nldf1 = nldf1%>%                    
  group_by(GSS_CODE)%>%         
  summarise(density =first(density),GSS_CODE=first(GSS_CODE),NAME = first(NAME), n = first(n))
```
Plot the density analysis result
```{r}
# plot the figure: The distribution of the density of the cycle lane/track

tmap_mode("view")
tm_shape(nldf1) +
  tm_polygons("density",
              style="jenks",
              alpha = 1,
              palette="PuOr",
              midpoint=NA,
              popup.vars=c("NAME","density"),
              title="Density per square kilometre"
              ) +
    tm_text("NAME", just = "top")+
  tm_shape(cycle_lane_slim) +
    tm_lines(col = "navy", alpha = 0.2)

# dcl_map = tm_shape(nldf1) +
#   tm_polygons("density",
#               style="jenks",
#               alpha = 1,
#               palette="PuOr",
#               midpoint=NA,
#               popup.vars=c("NAME","density"),
#               title="Density per square kilometre"
#               ) +
#     tm_text("NAME", just = "top")+
#   tm_shape(cycle_lane_slim) +
#     tm_lines(col = "navy", alpha = 0.2)
# tmap_save(dcl_map, "density_cycle_lane.html")

```

## 2.4 Descriptive Statistics

Introduce the ECharts4R, we plot the scatter chart in the beginning.
```{r}
library(echarts4r)
nldf1$n = as.numeric(nldf1$n)
nldf1$density = as.numeric(nldf1$density)

nldf2 = nldf1 %>%
  mutate(density = density * 1000)

nldf_scatter = nldf1 %>% 
  e_charts(n) %>% 
  e_scatter(n,density,NAME,name = "The Number of Cycling Lane") %>% 
  e_visual_map(n, scale = e_scale) %>% # scale color
  e_brush()%>%
  e_tooltip()%>%
  e_datazoom(x_index = 0, type = "slider") %>% 
  e_datazoom(y_index = 0, type = "slider")

htmlwidgets::saveWidget(nldf_scatter, file = "scatter.html")
```
the bar charts
```{r}
nldf_bar = nldf1 %>% 
  e_charts(NAME) %>% 
  e_bar(n, name = "Number",size = 5) %>% 
  e_bar(density, name = "Density",size = 5) %>% 
  e_title("Cycling Lane/Track") %>%
  e_tooltip()%>%
  e_flip_coords()
htmlwidgets::saveWidget(nldf_bar, file = "echarts4r.html")
```


# 3 The Exploration of Road Data

## 3.1 motorway junction
```{r}
london_motorway_junction = st_read(here("Dataset","Open Roads","openroads","London_MotorwayJunction.shp"))
plot(st_geometry(london_motorway_junction))
```

## 3.2 write the whole road link in London
```{r}

london_roadlink = st_read(here("Dataset","Open Roads","openroads","London_RoadLink.shp"))
plot(st_geometry(london_roadlink))
```

## 3.3 the road node in London
```{r}
london_roadnode = st_read(here("Dataset","Open Roads","openroads","London_RoadNode.shp"))
plot(st_geometry(london_roadnode))

# how to save map?
# visit the https://rdrr.io/cran/tmap/man/tmap_save.html
RN_Map = tmap_mode("view")
tm_shape(london_roadnode)+
  tm_dots(
    col = "blue",
    size = 0.002
    )
tmap_save(RN_Map, "London_RoadNode.html")
```

# Other Improvement

Introduce the new index: 
park2node = number_of_park_point / number_of_road_node
This index can reflect the completeness of in the street-relevant infrastructure

Firstly, we can count the park point for every LSOA

```{r}

library(CycleInfraLnd)
parking_point = get_cid_points(type = "cycle_parking")%>%
    st_transform(.,27700)

# the number of parking point
# npdf = ...
```

The analysis capacity of the street
I plan to use this [dataset](https://github.com/npalomin/streetspace_dataset_ldn)
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
   

